Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-02-12 latex/comp_or.tex
Dist from ramp door model infeasible

>>>>

\subsection{A possible improvement}

\cite{LurkinSchyns2015} considered an aircraft with two doors, and the minimization of loading and unloading costs at the intermediate node was modeled through a container sequencing problem. But, as both aircrafts dealt with in this work have only the ramp door, we tried to minimize the distance of travel of pallets inside the cargo bay, favoring unloading in the next node, by a post optimization of pallets positions to favor this distance minimization.
